
---
Red Wine Quality Exploration by Kelvin
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2) 
library(scales) 
library(GGally)
#install.packages("ggcorrplot")
#if(!require(devtools)) install.packages("devtools")
#devtools::install_github("kassambara/ggcorrplot")
library(ggcorrplot)  
#install.packages('memisc') 
library(memisc) 

```

```{r echo=FALSE, Load_the_Data}
# Load data ---------------------------
wine_data<-read.csv('wineQualityReds.csv')
dim(wine_data)
```

This report explores a dataset containing various properties which affact red 
wine quality for 1599 observations

# Univariate Plots Section

```{r echo=FALSE, Univariate_Plots}
set.seed(1000)
str(wine_data)
```

```{r echo=FALSE, warning=FALSE}
summary(wine_data)
```
Display a few observations
```{r echo=FALSE, warning=FALSE}
head(wine_data)
```
Display range of attribute X
```{r echo=FALSE, warning=FALSE}
range(wine_data$X)
```
Display length of unique values in X
```{r echo=FALSE, warning=FALSE}
length(unique(wine_data$X))
```

```{r echo=FALSE, warning=FALSE}
head(wine_data$X)
```
```{r echo=FALSE, warning=FALSE}
wine_data<-subset(wine_data, select = -c(X))
str(wine_data)
```
X attribute appears to be index of observations, 
it does not contain any meaningful insights, thus, removed 

```{r echo=FALSE, warning=FALSE}
qplot(wine_data$fixed.acidity,geom='histogram',binwidth=0.2,
      main='Histogram for fixed acidity',xlab='fixed acidity',
      fill=I('dark blue'),color=I('white'))
#boxplot(wine_data$fixed.acidity)
```

```{r echo=FALSE, warning=FALSE}
qplot(wine_data$volatile.acidity,geom='histogram',binwidth=0.02,
      main='Histogram for volatile acidity',xlab='volatile acidity', 
      fill=I('dark blue'),color=I('white'))

```
```{r echo=FALSE, warning=FALSE}
#refer to: https://stackoverflow.com/questions/4787332/how-to-remove-outliers-from-a-dataset
remove_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- NA
  y[x > (qnt[2] + H)] <- NA
  y
}  
qplot(remove_outliers(wine_data$volatile.acidity),geom='histogram',binwidth=0.02,
      main='Histogram for volatile acidity',xlab='volatile acidity', 
      fill=I('dark blue'),color=I('white'))
```
```{r echo=FALSE, warning=FALSE}

qplot(remove_outliers(wine_data$citric.acid),geom='histogram',binwidth=0.01,
      main='Histogram for citric acid',xlab='citric acid',
      fill=I('dark blue'),color=I('white'))

```

```{r echo=FALSE, warning=FALSE}
summary(wine_data$citric.acid)
```
Citric acid does not have a normal distribution and it 
tends to have most vauls fall between 0 and 0.75. However, its medians for each quality level
tends to go up as quality does.This makes me wonder what's relationship to the
quality.

```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$residual.sugar),geom='histogram',binwidth=0.1,
      main='Histogram for residual sugar',xlab='residual sugar', 
      fill=I('dark blue'),color=I('white'))
  
```
```{r echo=FALSE, warning=FALSE}
boxplot(remove_outliers(wine_data$residual.sugar)~wine_data$quality,
        data = wine_data,xlab='quality',ylab='residual.sugar')
  

```

```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$chlorides),geom='histogram',binwidth=0.001,
      main='Histogram for chlorides',xlab='chlorides', 
      fill=I('dark blue'),color=I('white'))
```

```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$free.sulfur.dioxide),geom='histogram',binwidth=1,
      main='Histogram for free sulfur dioxide',xlab='free sulfur dioxide', 
      fill=I('dark blue'),color=I('white'))
```
```{r echo=FALSE, warning=FALSE}
boxplot(remove_outliers(wine_data$free.sulfur.dioxide)~wine_data$quality,
        data = wine_data,xlab='quality',ylab='free sulfur dioxide')
  
```

```{r echo=FALSE, warning=FALSE}
summary(wine_data$free.sulfur.dioxide)

```

```{r echo=FALSE, warning=FALSE}
qplot(wine_data$total.sulfur.dioxide,geom='histogram',binwidth=0.05,
      main='Histogram for total sulfur dioxide',xlab='total sulfur dioxide log10', 
      fill=I('dark blue'),color=I('white'))+
  scale_x_log10()
```
```{r echo=FALSE, warning=FALSE}
boxplot(remove_outliers(wine_data$total.sulfur.dioxide)~wine_data$quality,
        data = wine_data,xlab='quality',ylab='total.sulfur.dioxide')
  

```
```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$density),geom='histogram',binwidth=0.0002,
      main='Histogram for density',xlab='density', 
      fill=I('dark blue'),color=I('white'))
```

```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$pH),geom='histogram',binwidth=0.02,
      main='Histogram for pH',xlab='pH', 
      fill=I('dark blue'),color=I('white'))
#    theme(plot.title = element_text(hjust = 0.5))
```

```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$sulphates),geom='histogram',binwidth=0.02,
      main='Histogram for sulphates',xlab='sulphates', 
      fill=I('dark blue'),color=I('white'))
```
```{r echo=FALSE, warning=FALSE}
boxplot(remove_outliers(wine_data$sulphates)~wine_data$quality,
        data = wine_data,xlab='quality',ylab='sulphates')
  

```
```{r echo=FALSE, warning=FALSE}
summary(wine_data$sulphates)
```

Most red wine contains sulphates bewteen 0.33 to 1, 
the median goes up as quality level does,which could indicate some kind relation.

```{r echo=FALSE, warning=FALSE}
qplot(remove_outliers(wine_data$alcohol),geom='histogram',binwidth=0.1,
      main='Histogram for alcohol',xlab='alcohol', 
      fill=I('dark blue'),color=I('white'))

```

Alchohol level skewed to the right, I'm curious about how it's connected to quality
```{r echo=FALSE, warning=FALSE}
boxplot(remove_outliers(wine_data$alcohol)~wine_data$quality,
        data = wine_data,xlab='quality',ylab='alcohol')
  
```

```{r echo=FALSE, warning=FALSE}
summary(wine_data$alcohol)
```

It appears that the most red wines have lower alcohol content.
and its median also goes up with quality level.


```{r echo=FALSE, warning=FALSE}
qplot(wine_data$quality,geom='histogram',binwidth=0.2,
      main='Histogram for quality',xlab='quality', 
      fill=I('dark blue'),color=I('white'),stat="count")

```


Quality attribute tends to be an categorical attribute, so I'd change it here to factor

```{r echo=FALSE, warning=FALSE}
#wine_data$quality<-factor(wine_data$quality) 
str(wine_data)
```

```{r echo=FALSE, warning=FALSE}
table(wine_data$quality)
```
Most of red wines have quality bewteen 4 to 7


# Univariate Analysis

### What is the structure of your dataset?

Dataset contains 13 variables and 1599 observations in total. 
All values are numbers and there are no missing values, however, 
variable X is intended to indexing, containing no meaningful insights,
thus, it was removed from dataset
Other findings: 

  1.Most red wines' quality fall bewteen 4 and 7, larger value stands 
    for better quality
    
  2.Many variables have outliers 
  
  3.Some variables are skewed such as free.sulfur.dioxide
  
  4.Some variables are not in normal distribution such as citric.acid and alcohol
  
These should be further analyzed later

### What is/are the main feature(s) of interest in your dataset?

The main feature is quality and influential ones such as citric acidity,sulphates and alcohol.
I will investigate more on which features have stronger relationship with quality. 

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

Every other 11 features are considered contributor in this dataset and will
be carefully examined later to find out more insights

### Did you create any new variables from existing variables in the dataset?

No

### Of the features you investigated, were there any unusual distributions? \

yes, citric.acid does not seem to have a regular distribution and
it reminds almost evenly for the rest.

### Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

yes, I removed varable X which is meant to be index of dataset, thus it contains no 
meaningful insight.

# Bivariate Plots Section

```{r echo=FALSE}
corr=cor(wine_data)
round(corr,2)
```


```{r  echo=FALSE, Bivariate_Plots}

ggcorrplot(corr,
   lab = TRUE,lab_size=2,legend.title = 'Correlation') 
```

By analyzing correlation matrix above, quality seems highly correlated to alcohol, sulphates 
and citric.acid. In addition, fixed.acidity is highly correlated to density and cirtic
acid. Total.sulfer.dioxide is highly corralated to free.sulfuer.dioxide which is 
understandable since total.sulfer.dioxide consists of free.sulfer.dioxide and bond sulfer
dioxide.

```{r  echo=FALSE, message=FALSE, warning=FALSE}

ggplot(aes(y=remove_outliers(wine_data$citric.acid),x=as.factor(wine_data$quality)),data=wine_data)+
  geom_boxplot()+
  geom_smooth(method = "lm",se=FALSE,aes(group=1))+
  xlab('quality')+
  ylab('citric.acid')
```

Based on plot above, it is apparent that medians of quality levels increases as citric acid increases too.


```{r  echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(y=remove_outliers(wine_data$alcohol),x=as.factor(wine_data$quality)),data=wine_data)+
  geom_boxplot()+
  geom_smooth(method = "lm",se=FALSE,aes(group=1))+  
  xlab('quality')+
  ylab('alcohol')
  
```

Based on plot above, alcohol does not have a linear relationship with quality although they are highly 
correlated.

```{r  echo=FALSE,  message=FALSE, warning=FALSE}
ggplot(aes(y=remove_outliers(wine_data$volatile.acidity),x=as.factor(wine_data$quality)),data=wine_data)+
  geom_boxplot()+
  geom_smooth(method = "lm",se=FALSE,aes(group=1))+  ylab('quality')+
  ylab('volatile.acidity')+
  xlab('Quality')+
  geom_smooth()
  
```

Based on plot above, quality increases as volatile acidity decreases, they are in a negative relationship.

```{r  echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(y=remove_outliers(wine_data$sulphates),x=as.factor(wine_data$quality)),data=wine_data)+
  geom_boxplot()+
  geom_smooth(method = "lm",se=FALSE,aes(group=1))+
  xlab('quality')+
  ylab('sulphates')+
  geom_smooth()

```

The above suggests that the highly quality increases while correlated sulphates increases. 

```{r  echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=wine_data$free.sulfur.dioxide,y=wine_data$total.sulfur.dioxide),data=wine_data)+
  geom_jitter(alpha=1/2,fill=I('#F79420'),color=I('black'),shape=21)+
  xlab('free sulfur dioxide')+
  ylab('total sulfur dioxide')+
  scale_y_continuous(lim=c(0,175))+
  geom_smooth(method="lm")
```

The above figure indicates that total sulfur dioxide is highly related to free sulfur dioxide in a 
linear relationship

``````{r  echo=FALSE}
m1 <- lm(wine_data$total.sulfur.dioxide ~ wine_data$free.sulfur.dioxide,data = wine_data)
summary(m1)
```


```{r  echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=wine_data$density,y=wine_data$residual.sugar),data=wine_data)+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+
  xlab('residual.sugar')+
  ylab('density')+
  geom_smooth()
```

density vs residual sugar seem have some outliers that affact estimate here, so let's remove outliers.


```{r  echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(y=remove_outliers(wine_data$density),x=remove_outliers(wine_data$residual.sugar)),data=wine_data)+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21,position='jitter',alpha=1/2)+
  xlab('residual.sugar')+
  ylab('density')+
  geom_smooth()
```

The above figures show relationship between density and residual sugar
density ~ residual sugar seem forming linear relationship 
but a close look reveals that outliers influenced estimate. 
After removing outliers, no strong relationship seems obvious between density and residual sugar

```{r  echo=FALSE,  message=FALSE, warning=FALSE}
ggplot(aes(x=remove_outliers(wine_data$citric.acid),y=remove_outliers(wine_data$residual.sugar)),data=wine_data)+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+
  xlab('residual.sugar')+
  ylab('citric.acid')+
  geom_smooth()
```

```{r  echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(y=wine_data$pH,x=wine_data$fixed.acidity),data=wine_data)+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+
  xlab('fixed.acidity')+
  ylab('pH')+
  geom_smooth(method="lm")
```

It is obvious that pH is highly related to fixed acidity in a linear relationship.

``````{r  echo=FALSE}
m2 <- lm(wine_data$pH ~ wine_data$fixed.acidity,data = wine_data)
summary(m2)
```

```{r  echo=FALSE, message=FALSE, warning=FALSE}

ggplot(aes(y=wine_data$pH,x=remove_outliers(wine_data$citric.acid)),data=wine_data)+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+
  xlab('citric.acid')+
  ylab('pH')+
  geom_smooth(method="lm")
```

From above plot, pH is also highly related to citric acid in a negative linear relationship.

```{r  echo=FALSE}

m3 <- lm(wine_data$pH ~ wine_data$citric.acid,data=wine_data)
summary(m3)

```

The above two model indicates that pH has linear relationship with citric acid and fixed acidity

```{r  echo=FALSE, message=FALSE}

ggplot(aes(y=wine_data$pH,x=wine_data$free.sulfur.dioxide),data=wine_data)+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+
  xlab('free.sulfur.dioxide')+
  ylab('pH')+
  geom_smooth(method="lm")
```

On the other hand, free sulfur dioxide does not have strong linear relationship with pH as above plot
shows.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

The quality does have high correlation with alcohol, citric acid and sulphates. 
However, there are no strong linear relationships among them as figures show in above section.
On the other hand, some relationships exist among other features such as pH vs citric acid, 
pH vs fixed acidity and free sulfur dioxide vs total sulfur dioxide. Those pairs all have noticeable
linear relationships.


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

pH has strong negative relationship with fixed acidity and citric acid while total sulfur 
dioxide seems having strong positive relationship with free sulfur dioxide. Further study shows 
that total sulfur dioxide consists of free sulfur dioxide and bond sulfur dioxde.


### What was the strongest relationship you found?

The strongest relationship is between pH and fixed acidity, they are in a negative linear relationship.


# Multivariate Plots Section


```{r echo=FALSE,message=FALSE, Multivariate_Plots}
y<-wine_data$pH
x<-wine_data$fixed.acidity
z<-factor(wine_data$quality)

ggplot(wine_data,aes(x=x,y=y,color=z))+
  geom_point(position='jitter',alpha=1/2)+
  labs(x="fixed acidity",y="pH",title="Quality of pH vs fixed acidity")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))+
  scale_x_continuous(breaks = seq(4,16,1))+
    guides(color=guide_legend(title="Quality",title.theme = element_text(size = 15,angle=0)))+
scale_color_manual(values=c("#04e24a", "#b504e2", "#2104e2","#e27e04","#cc0c0c","black"))



```

The above plot demostrates pH decreases as fixed acidity increases, it is apparent that pH and fixed acidity fall into a negative linear relationship, while quality does not follow. the quality of red wine seems spread across plot in a random manner. 


```{r echo=FALSE,message=FALSE,warning=FALSE}

x <- factor(wine_data$quality) 
y <- wine_data$fixed.acidity 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ 
  geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ 
  geom_jitter(aes(x=factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="fixed acidity",title="fixed acidity vs quality")
```

Further breaking into quality and fixed acidity plot, it is clear that quality and fixed acidity are in a weak linear relationship, because medians flucutates up and down. 

```{r echo=FALSE,message=FALSE,warning=FALSE}

x <- as.factor(wine_data$quality) 
y <- wine_data$pH 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="pH",title="pH vs quality")
```

From above plot, I can tell that pH values tend to decrease as quality increases in a negatived linear relationship which is stranger than fixed acidity vs quality.


```{r echo=FALSE,message=FALSE,warning=FALSE}

y<-wine_data$pH
x<-wine_data$citric.acid
z<-factor(wine_data$quality)

ggplot(wine_data,aes(x=x,y=y,color=z))+
  geom_point(position='jitter',alpha=1/2)+
  labs(x="citric acidity",y="pH",title="Quality of pH vs citric acidity")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))+
    guides(color=guide_legend(title="Quality",title.theme = element_text(size = 15,angle=0)))+
scale_color_manual(values=c("#04e24a", "#b504e2", "#2104e2","#e27e04","#cc0c0c","black"))



```

The above plot demostrates pH decreases as citric acidity increases, it is apparent that pH and fixed acidity fall into a negative linear relationship as well, while quality also does not follow their relation. the quality seems spreading across plot in a random manner. 


```{r echo=FALSE,message=FALSE,warning=FALSE}

x <- factor(wine_data$quality) 
y <- wine_data$citric.acid 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="citric acidity",title="citric acidity vs quality")
```

While looking at plot above, it is very clear that citric acidity is in a positive linear relationship with quality since medians go up as quality level increases. 

```{r echo=FALSE,message=FALSE,warning=FALSE}

x<-wine_data$alcohol
y<-wine_data$density
z<-factor(wine_data$quality)

ggplot(wine_data,aes(x=x,y=y,color=z))+
  geom_point(position='jitter',alpha=1/2)+
  labs(y="density",x="alcohol",title="Quality of density vs alcohol")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))+
    guides(color=guide_legend(title="Quality",title.theme = element_text(size = 15,angle=0)))+
scale_color_manual(values=c("#04e24a", "#b504e2", "#2104e2","#e27e04","#cc0c0c","black"))


```

The above plot demostrates density decreases as alcohol increases, it is apparent that density and alcohol fall into a negative linear relationship, while quality does not follow. the quality seems spreading across plot in a random manner. 


```{r echo=FALSE,message=FALSE,warning=FALSE}
x <- as.factor(wine_data$quality) 
y <- wine_data$alcohol 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ 
  geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="alcohol",title="alcohol vs quality")
```

Further breaking into alcohol vs quality plot, for low level quality, alcohol does not seem related to quality, however,
from medium to high level, quality and alcohol are obviously highly related.

```{r echo=FALSE,message=FALSE,warning=FALSE}

x <- as.factor(wine_data$quality) 
y <- wine_data$density 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="density",title="density vs quality")
```

Breaking into density and quality plot, I cannot see a strong relationship. 


```{r echo=FALSE,message=FALSE,warning=FALSE}

x<-wine_data$free.sulfur.dioxide
y<-wine_data$total.sulfur.dioxide
z<-factor(wine_data$quality)

ggplot(wine_data,aes(x=x,y=y,color=z))+
  geom_point(position='jitter',alpha=1/2)+
  labs(y="total.sulfur.dioxide",x="free.sulfur.dioxide",title="Quality of free.sulfur.dioxide vs total.sulfur.dioxide")+
  theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold"))+
    guides(color=guide_legend(title="Quality",title.theme = element_text(size = 15,angle=0)))+
scale_color_manual(values=c("#04e24a", "#b504e2", "#2104e2","#e27e04","#cc0c0c","black"))+
  ylim(0,170)


```

The above plot demostrates total.sulfur.dioxide increases as free.sulfur.dioxide increases, it is apparent that total.sulfur.dioxide and free.sulfur.dioxide fall into a positive linear relationship, while quality does not follow. the quality of red wine seems spreading across plot in a random manner. 


```{r echo=FALSE,message=FALSE,warning=FALSE}
#because free.sulfur.dioxide is part of total.sulfur.dioxide, i will use their ratio instead
x <- factor(wine_data$quality) 
y <- wine_data$free.sulfur.dioxide/wine_data$total.sulfur.dioxide
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="sulfur percentage",title="sulfur percentage vs quality")

```

Since free.sulfur.dioxide and total.sulfur.dioxide are highly related, and total.sulfur.dioxide contains free.sulfur.dioxide, I can use ratio of free.sulfur.dioxide over total.sulfur.dioxide to represent the feature. The above plot indicates that there are no linear relationship between percentage of sulfer and quality. Out of 12 variables some have linear relationships with quality, therefore, I can try to create a linear model as following.

```{r echo=FALSE,message=FALSE,warning=FALSE}
#based on above analysis, i can create a linear model as following
r<-wine_data$free.sulfur.dioxide/wine_data$total.sulfur.dioxide
f<-wine_data$fixed.acidity
q<-wine_data$quality
a<-wine_data$alcohol
c<-wine_data$citric.acid
p<-wine_data$pH
m1<-lm(q~r,data=wine_data)
m2<-update(m1,~.+f)
m3<-update(m2,~.+a)
m4<-update(m3,~.+p)
m5<-update(m4,~.+c)
mtable(m1,m2,m3,m4,m5,sdigits=3)
```


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

free.sulfur.dioxide,alcohol,citric.aci and total.sulfur.dioxide have strong correlation in a
linear relationship.fixed.acidity and pH are other variables that moderately to quality, 
it seems they have weaker relationships and one thing noticeable is that pH is in a negative 
linear relationship with quality variable


### Were there any interesting or surprising interactions between features?

It is interesting and surprising that the quality also relates to pH value in a negative linear
relationship. Also, alcohol level seems to play a part in quality of red wine, it is surprising to 
know that more alcohol better quality it becomes, but I'd assume alcohol level will max out its 
influence at some point. 



### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

Yes, I did. the model created starts with percentage of sulfur and quality.
By adding fixed acidity, citric acid, and pH, model gets improved moderately.


------

# Final Plots and Summary

### Plot One

```{r echo=FALSE, Plot_One}
x <- as.factor(wine_data$quality) 
y <- wine_data$alcohol 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+labs(x="quality",y="alcohol",title="Alcohol vs Quality") 
```


### Description One

Alcohol level plays an essential role in quality, starting from median quality the influence of alcohol becomes 
clearer than lower end of of quality.


### Plot Two

```{r echo=FALSE, Plot_Two}
y<-wine_data$pH
x<-wine_data$fixed.acidity
z<-factor(wine_data$quality)

ggplot(wine_data,aes(x=x,y=y,color=z))+
  geom_point(position='jitter',alpha=1/2)+
  labs(x="fixed acidity",y="pH",title="Quality of pH vs fixed acidity")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))+
  scale_x_continuous(breaks = seq(4,16,1))+
    guides(color=guide_legend(title="Quality",title.theme = element_text(size = 15,angle=0)))+
scale_color_manual(values=c("#04e24a", "#b504e2", "#2104e2","#e27e04","#cc0c0c","black"))


```


```{r echo=FALSE,message=FALSE,warning=FALSE}

x <- as.factor(wine_data$quality) 
y <- wine_data$pH 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="pH",title="PH vs Quality")

```


### Description Two

It is obvious that pH decreases with fixed acidity becomes larger. In addition, pH decreases with quality as well.

### Plot Three

```{r echo=FALSE, warning=FALSE,Plot_Three}

x <- as.factor(wine_data$quality) 
y <- wine_data$citric.acid 
df <- data.frame(x=x,y=y) 
ggplot()+ geom_boxplot(aes(x=as.factor(x),y=y),data = df)+ geom_smooth(method = "lm", formula=y~as.numeric(x), aes(x=as.numeric(x), y=y), data = df )+ geom_jitter(aes(x=as.factor(x),y=y) ,alpha = 0.2,color='orange',data = df)+
  labs(x="quality",y="citric acidity",title="Quality vs Citric Acid")
 
```

### Description Three
citric acidity has strong relationship with quality in this case. As median of citiric acidity goes bigger,
quality becomes better too. It is surprising that quality is related to citric acidity in red wine.
------

# Reflection
The redwineQuality dataset contains 1599 observations and 12 variables with index column X, and quality variable as class.
I started by looking at each individual variables and exploring some interesting features with histdigrams. 
Then, I looked at relations between pairs of variables to further understand where the relationships are. At the end, 
I ploted multivariate diagrams to get better understanding of relations among those chosen variables. 

There are not very strong relationships, I had difficulties at beginning to understand them, but moderate relations between some variables such as total.sulfur.dioxide vs free.sulfur.dioxide, pH vs quality alcohol vs quality and so on are later found from plots. It is surprising that citric.acid also plays an essential role in making high quality red wine. With those that highly relate to quality I created a linear model. It is however limited to the amount of data, and it could be improved if there are more observations in dataset.



